Fourmile Calibrations

### 2023-03-16 calibration_output.Rmd
hd fig updates

```{r catch precip, echo = F}
setwd("./catchment_output")

@@

catchment_mo_max <- catchment %>%
  mutate(month = month(time)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ max(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_max = precip, tmax_max = tmean, 
                solrad_max = solRad, rh_max = rhum)

catchment_mo_min <- catchment %>%
  mutate(month = month(time)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ min(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_min = precip, tmin_min = tmean, 
                solrad_min = solRad, rh_min = rhum)

catchment_mo <- left_join(catchment_mo_mean, catchment_mo_max, 
                          by = c('month', 'site'))

catchment_mo2 <- left_join(catchment_mo, catchment_mo_min, 
                          by = c('month', 'site')) %>%
  mutate(month_name = month.abb[month]) %>%
  mutate(month_name = factor(month_name, 
                             levels = c('Jan', 'Feb', 'Mar',
                                        'Apr', 'May', 'Jun',
                                        'Jul', 'Aug', 'Sep',
                                        'Oct', 'Nov', 'Dec')))

p_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = precip_min, ymax = precip_max, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw() +
  labs(y = 'Precipitation (mm)') +
  ggtitle('B')

p_moplot

t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = tmin_min, ymax = tmax_max, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw() +
  labs(y = expression("Mean temperature " ( degree~C)))+
  ggtitle('C')

@@

sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = solrad_min, ymax = solrad_max, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw() +
  labs(y = 'Solar Radiation (unit)') +
  ggtitle('D')

@@

rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = rh_min, ymax = rh_max, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw() +
  labs(y = 'RH (%)', x= 'Month') +
  ggtitle('E')

rh_moplot

ggarrange(p_moplot+ rremove("x.text") +
               rremove("x.title") +
               rremove('x.ticks'),
             t_moplot+ rremove("x.text") +
               rremove("x.title")+
               rremove('x.ticks'), 
             sol_moplot + rremove("x.text") +
               rremove("x.title")+
               rremove('x.ticks'),
             rh_moplot,
          common.legend = T,
          legend = 'bottom',
             nrow = 4)

>>>>

```{r catch precip, echo = F}
setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output")

@@

catchment_mo_sd <- catchment %>%
  mutate(month = month(time)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ sd(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_sd = precip, tmean_sd = tmean, 
                solrad_sd = solRad, rh_sd = rhum)

catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd, 
                          by = c('month', 'site'))

catchment_mo2 <- catchment_mo %>%
  mutate(month_name = month.abb[month]) %>%
  mutate(month_name = factor(month_name, 
                             levels = c('Jan', 'Feb', 'Mar',
                                        'Apr', 'May', 'Jun',
                                        'Jul', 'Aug', 'Sep',
                                        'Oct', 'Nov', 'Dec')))

p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean,
                          color = site, fill = site)) +
  geom_col(position='dodge') +
  geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd), 
                position = position_dodge(width = 0.6), width = 0.2) +
  theme_bw(base_size = 14) +
  labs(y = 'Precipitation (mm)',
       x = element_blank())

ggsave("P.png", plot = p_cols, width = 8, height = 6, dpi = 300)

t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw(base_size=14) +
  labs(y = expression("Mean temperature " ( degree~C)),
       x = element_blank())

@@

sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw(base_size = 14) +
  labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
       x = element_blank())

@@

rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw(base_size = 14) +
  labs(y = 'RH (%)', x= element_blank()) 
rh_moplot

quad <- ggarrange(p_cols, 
          t_moplot,
          sol_moplot,
          rh_moplot,
          common.legend = T,
          legend = 'bottom',
             nrow = 2,
          ncol= 2)

ggsave("quad.png", plot = quad, width = 8, height = 6, dpi = 300)
